\plaintitle

### 2018-04-05 paper/paper.tex
...

% 部屋を暗くする
% make the room darker 
% iot ......

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  %
  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
  % he may have to translate his intention into an English expression ``make the room darker'',
  he may have to find that he should ``turn off the ceiling light'' for the task,
  translate it to a required action ``toggle the wall switch''
  or a command like ``\tt{\$ iot clight 0}''.
  %
  % When a user wants to ``make the room darker'',
  % he should translate it to a real action like ``turn off the ceiling light''.
  % To do so,
  % he may have to ``toggle the wall switch''
  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  % If the user is a Chinese speaker, he might have to translate his intention
  % ``房間暗一点'' into ``make the room darker'',
  % ``turn off the ceiling light'', 
  % ``toggle the wall switch'',
  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
  %
  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.
\end{abstract}

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use \tt{git} with an argument
``\verb|HEAD^^|''
for specifying the old version.

@@

A description like ``2 days ago'' is also shown in the candidate list.
This means that the user can use the same string \sqtt{git RE 2}
for getting the \stt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
may not be familiar to most \tt{git} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.

A Japanese \stt{git} user can do the same thing just like
English-speaking users.
He can user the term \qtt{比}(compare) to find how he can perfor the job.

\begin{figure}[H]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

@@

\begin{figure}[htb]
\begin{verbatim}
\end{verbatim}
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
\caption{A {\SB} page for \tt{git diff}.}
\label{scrapboxpage}
\end{figure}

@@

% {\EH} search algorithm and database structure

@@

A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.

Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents the help entry description
and a corresponding command pattern.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands or calling library functions
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be like this:

@@

The first regular expression, the description part,
is for generating texts like
\sqsf{Compare README.md with the one from 1 versions before}, 
\sqsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a \tt{git} command.
In the first example, \sqsf{README.md} and \sqsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.

@@

can be used for Japanese users.
In this case,
\sqsf{README.mdを1個前のものと比較する},
\sqsf{README.mdを2個前のものと比較する}, etc.
are used for theh matching.

@@

Finding appropriate entries from the huge help document space is performed in two steps.
First, we parse the regular expression to
generate a state transition diagram that represents all the strings represented
in the regular expression.
Second, we generate all the description strings by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

The ``shifter algorithm''\cite{Wu:1992:FTS:135239.135244}
is a simple and efficient
text search algorithm which has interesting features
not found in more common pattern matching algorithms like
KMP\cite{KMP}, Boyer-Moor\cite{Boyer:1977:FSS:359842.359859}, etc.

When a user wants to find a word \qsf{README} in a text,
he can use a patter matching state machine like below,
where the gray circle denotes that the state is active.

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme1.pdf}
\caption{A state machine for \qsf{README}.}
\label{readme1}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme2.pdf}
\caption{After receiving \qsf{R}.}
\label{readme2}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=70mm,bb=0 0 439 73]{figures/readme3.pdf}
\caption{After receiving \qsf{README}.}
\label{readme3}
\end{figure}

@@

%   *  ** 
%  risto rante
%  restaurant
\begin{figure}[htb]
\begin{verbatim}
\end{verbatim}
\centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
\caption{Matching error between \qsf{README} and \qsf{REDDY}.}
\label{readme-reddy-mismatch}
\end{figure}

Adding three more states to Figure \ref{readme1}, we can perform more
sophisticated pattern matcher which can accept strings with
0 to 3 matching errors.

\begin{figure}[htb]
\includegraphics[width=85mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
\caption{A pattern matcher accepting 0-3 errors.}
\label{shifterambig}
\end{figure}

@@

The data used in {\GH} are represented as ``{\SB}'' documents.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors,
using simple markup symbols.

@@

This page describes the usage of \sqtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the description of \sqtt{git diff}.
%
% Specs and command lines are specified with a special symbol, and
% all other documents can be written just like standard manuals and help documents.

Although usage examples are often shown on Unix man pages,
they cannot be used as the database of online help system.
On the other hand,
a {\SB} document contains both the manual page and the help database
at the same place.
%
This strategy is similar to the
``Literate Programming''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
} style,
where source codes and documents are put in the same document.

@@

IMs are very popular in the world these days,
and it is very common for people to 
use translation systems for using computers.
Using an additional translation system like {\GH} is ...

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \sqtt{la} on the Unix shell,
\sqtt{latex}, \sqtt{latex}, and other commands are shown as candidates.
When a user types \sqtt{ls RE} and types the TAB key,
Unix shell checks the directory, find the \stt{README.md} file, and
replace the user's input with \sqtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in text editors and command line editors.

@@

% Programing-by-Example (PBE) systems\cite{Cypher}\cite{Lieberman}.

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps \tt{git} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

@@

Many smart IDEs for suggesting codes have been proposed resently.

% 賢い補完
Little's system\cite{Little:2006:TKC:1166253.1166275}
generates a complete JavaScript code snippet from keyword fragments.
For example,
\sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
can be generated from keywords like
\sqsf{left},
\sqsf{margin},
\sqsf{4}, and
\sqsf{inches}.
The system generates the code using a template database and heuristics
for the target system.
It is useful for a special environment, but
users of the system cannot modify the algorithm or the database
even when appropriate suggestions cannot be give by the system.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a snippet like \sqtt{chooser. showOpenDialog()}
can be generated from the keyword
\sqsf{ch} and\sqsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \sqtt{chooser}, \sqtt{dialog}),
and large code example corpus should exist before

@@

\section{Evaluation}

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{paper}

>>>>

% 4/5 17:00 PDT = 4/6 9:00 JST

% 部屋を暗くする
% make the room darker

@@

\def\GH{\textsf{GitHelp}}
\def\SB{\textsf{Scrapbox}}
\def\EH{\textsf{ExpandHelp}}
\def\GIT{\texttt{git}}
\long\def\tt#1{\texttt{#1}}
\long\def\stt#1{\texttt{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\sf#1{\textsf{#1}}
\long\def\ssf#1{\textsf{\fontsize{9pt}{0pt}\selectfont{#1}}}
\long\def\qtt#1{``\tt{#1}''}   % quote tt
\long\def\sqtt#1{``\stt{#1}''} % smal quote tt
\long\def\qsf#1{``\sf{#1}''}
\long\def\sqsf#1{``\ssf{#1}''}
\long\def\qit#1{``\textit{#1}''}

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  %
  For example, when a Chinese person wants to ``房間暗一点'' (make the room darker),
  % he may have to translate his intention into an English expression ``make the room darker'',
  he may have to find that he should ``turn off the ceiling light'' for the task,
  translate it to a required action ``toggle the wall switch''
  or a command like ``\tt{\$ iot clight 0}''.
  %
  % When a user wants to ``make the room darker'',
  % he should translate it to a real action like ``turn off the ceiling light''.
  % To do so,
  % he may have to ``toggle the wall switch''
  % or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  % If the user is a Chinese speaker, he might have to translate his intention
  % ``房間暗一点'' into ``make the room darker'',
  % ``turn off the ceiling light'', 
  % ``toggle the wall switch'',
  % and finally to a command like ``\tt{\$ iot ceilinglight 0}''.
  %
  There is a huge gap between ``房間暗'' and ``\tt{\$ iot clight 0}'', and
  people are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex {\GIT} commands
  from fragments of users' intentions.
\end{abstract}

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete {\GIT} command
using the {\EH} framework.

@@

When a user wants to compare the latest \tt{README.md} file
with the same file from 2 versions before,
he might try to use {\GIT} with an argument
``\verb|HEAD^^|''
for specifying the old version.

@@

A description like \sqsf{2 days ago} is also shown in the candidate list.
This means that the user can use the same string \sqtt{git RE 2}
for getting the \stt{README.md} file of the day before yesterday.
The command,
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff '@{2 days ago}' README.md|}'',
may not be familiar to most {\GIT} users,
but users can perform this task only by giving \sqtt{RE} and \sqtt{2}.

A Japanese {\GIT} user can do the same thing just like
English-speaking users.
He can user the term \qtt{比}(compare) to find how he can perfor the job.

\begin{figure}[t]
  % \includegraphics[width=10cm,bb=0 0 1290 866]{figures/githelp1.png}
  \includegraphics[width=12cm,bb=-100 -100 1190 766]{figures/githelp1.png}
  \caption{Invoking {\GH}.}
  \label{bash2}
\end{figure}

@@

\begin{figure}[b]
\begin{verbatim}
\end{verbatim}
% \centerline{\includegraphics[width=100mm,bb=0 0 1428 1288]{figures/scrapbox1.png}}
\centerline{\includegraphics[width=100mm,bb=-50 -50 1000 900]{figures/scrapbox1.png}}
\caption{A {\SB} page for \tt{git diff}.}
\label{scrapboxpage}
\end{figure}

@@

@@

A flexible information retrieval mechanism ``{\EH}'' is used in {\GH}.
%
Help data used in {\EH} are provided as a set of data entries
consisting of a regular expression that represents the help entry description
and a corresponding command pattern string.
A description string is used to produce natural language texts
that are easily understandable by users,
while command patterns are used for invoking commands
corresponding to the description.
%
For example, a help entry for showing the difference between
current file and older file can be like this:

@@

The first regular expression, the description part,
is for generating texts like
\sqsf{Compare README.md with the one from 1 versions before}, 
\sqsf{Compare index.html with the one from 2 versions before}, etc.,
and the second part, command part,
is used to generate a command to execute a {\GIT} command.
In the first example, \sqsf{README.md} and \sqsf{1}
match the first and second parentheses of the regular expression, and
these values are assigned to \tt{\$1} and \tt{\$2}
for the command part, generating a command
``{\fontsize{9pt}{0pt}\selectfont\verb|$ git diff $(git rev-list -n #{$2} HEAD -- #{$1})^ -- #{$1}|}''.

@@

can be used for Japanese users.
In this case,
\sqsf{README.mdを1個前のものと比較する},
\sqsf{README.mdを2個前のものと比較する}, etc.
are used for the matching.

@@

Finding appropriate entries from the huge help document space is performed in two steps.
First, a state transition diagram is generated from the regular expressions
used in the descriptions.
Second, all the description strings are generated by expanding the regular expression
into a tree, and filter the generated strings by the pattern specified by the user.
Efficient pattern matching is performed every time a new description text is generated,
and only the best-matched descriptions are shown to the user as menu entries.
We call this the ``\textit{generate-and-filter}'' technique,
and we will describe the details later.

@@

The ``shifter algorithm''\cite{Wu:1992:FTS:135239.135244}
is a simple and efficient
text search algorithm that has interesting features
not found in more common pattern matching algorithms like
KMP\cite{KMP}, Boyer-Moor\cite{Boyer:1977:FSS:359842.359859}, etc.

When a user wants to find a word \sqsf{README} in a text,
he can use a patter matching state machine like below,
where the gray circle denotes that the state is active.

\begin{figure}[h]
  \includegraphics[width=60mm,bb=0 0 439 73]{figures/readme1.pdf}
  \caption{A state machine for \qsf{README}.}
  \label{readme1}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme2.pdf}
\caption{After receiving \qsf{R}.}
\label{readme2}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=60mm,bb=0 0 439 73]{figures/readme3.pdf}
\caption{After receiving \qsf{README}.}
\label{readme3}
\end{figure}

@@

%   *  ** 
%  risto rante
%  restaurant
\begin{figure}[htb]
  \centerline{\includegraphics[width=40mm,bb=0 0 104 51]{figures/readme-mismatch.pdf}}
  \caption{Matching error between \qsf{README} and \qsf{REDDY}.}
  \label{readme-reddy-mismatch}
\end{figure}

Adding three more states to Figure \ref{readme1}, we can perform more
flexible pattern matcher which can accept strings with
0 to 3 matching errors.

\begin{figure}[htb]
  \includegraphics[width=65mm,bb=0 0 443 282]{figures/readme-ambig.pdf}
  \caption{A pattern matcher accepting 0-3 errors.}
  \label{shifterambig}
\end{figure}

@@

The data used in {\GH} are represented as ``{\SB}'' documents.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like using text editors.

@@

This page shows how to use \sqtt{git diff}, and
the page contains command specifications in {\EH} format
in addition to the documentation.

% Specs and command lines are specified with a special symbol, and
% all other documents can be written just like standard manuals and help documents.

Usage examples are often shown on documents and manuals like Unix man pages,
they cannot be used as the database of an online help system.
On the other hand,
a {\SB} document contains both the manual document and the help database
in the same place, just like
writing a source code and the document in the same place
using the ``Literate Programming''\footnote{
  \ssf{https:{\slash}{\slash}en.wikipedia.org{\slash}wiki{\slash}Literate\_programming}
} style.

@@

IMs are very popular in the world these days,
and it is very common for people to 
use translation systems for using computers.

The behavior of {\GH} is similar to conventional IMs.

@@

On text editors and Unix shells,
``text completion'' has been available for a long time.
%
When a user types the TAB key after typing \sqtt{la} on the Unix shell,
\sqtt{latex}, \sqtt{latex}, and other Unix commands are shown as candidates.
When a user types \sqtt{ls RE} and types the TAB key,
the shell checks the directory, find the \stt{README.md} file, and
replace the user's input with \sqtt{ls README.md}.
This behavior is called ``text completion'', and many variations of
this idea have been proposed and adopted in command shells and text editors.

@@

Gitsome\footnote{\textsf{https:{\slash}{\slash}github.com{\slash}donnemartin{\slash}gitsome}}
helps {\GIT} users by
dynamically showing possible arguments and related manuals on the Unix shell,
just like {\GH}.
The goal of Gitsome is alomost the same as {\GH} and we agree with its concept,
but Gitsome does not support ...

@@

Integrated Development Environments (IDEs) are widely used for
software development, and
many smart IDEs for suggesting codes have been proposed resently.

Little's system\cite{Little:2006:TKC:1166253.1166275}
generates a complete JavaScript code snippet from keyword fragments
give by users.
For example, a code snippet
\sqtt{ActiveDocument .PageSetup .LeftMargin = InchesToPoints(2)}
can be generated from keywords like
\sqsf{left},
\sqsf{margin},
\sqsf{inches},
and \sqsf{2}.
The system generates the code using a template database and heuristics
designed for the target system.
It is useful for a specific environment, but
users of the system cannot modify the algorithm or the database
even when appropriate suggestions cannot be give by the system.

@@

Han's Abbreviation Completion system\cite{Han:2009:CCA:1747491.1747530}
can generate a code snippet from abbreviation strings give by the user.
For example, a code snippet like \sqtt{chooser. showOpenDialog()}
can be generated from strings like
\sqsf{ch} and \sqsf{opn}, using the code database and HMM.
It can be very useful as a shorthand for handling long names,
but users should have a vague knowledge about the correct names
(e.g. \sqtt{chooser}, \sqtt{dialog}),
and large code example corpus should exist before

@@

\section{Discussions}

Since the translation mechanism of {\EH} is simple and flexible,
it can be used for a wide range of application domains where
intelligent help is required.
{\EH} can be used for

\paragraph{Order of command and arguments}

Using a command shell,
users have to enter a command first and enter options and arguments after that.
Using a GUI desktop,
users can right-click a data icon to show a menu,
and select what he wants to do from the menu.
Switching between command-oriented usage pattern and
data-oriented usage pattern is sometimes confusing.
Using {\EH}, users can find what they can do
either by specifying commands or by specifying data, 
without worrying about the order.

\paragraph{Usage of regular expressions}

An advantage of using a regular expression is that
it is fairly easy for users to write description texts.
People can easily write a help description like
\sqtt{(Start|Run) Firefox browser}
without having a knowledge of automata or formal grammar.
We can use arbitrary texts for the database of Expand Help.
For example,
we can collect hundreds of books titled ``Windows tips'' from the market
and convert all the title of the tips into help data of ExpandHelp.

\paragraph{Toward more general help system}

Since a user can activate a command or access a Web page
from ExpandHelp only by typing keywords,
it can be used as a command launcher rather than a help system.
Adding data to an existing help system is usually a hard task,
but adding data so ExpandHelp is very simple.
It would also be convenient to use a Wiki page for providing the help
data for ExpandHelp, since users can easily edit the description
for their needs.
We are planning to distribute Wiki-based ExpandHelp to the public and
share the help data between groups of people.

@@

We have introduced a general-purpose flexible translation framework {\EH}
and used it for {\GH}, a system for supporting {\GIT} users.
%
The database of {\EH} are shared on a real-time general-purpose Wiki system {\SB},
and all the users can share it to improve the quality of the help system.

Unlike existing smart IDEs for supporting programming tasks,
{\EH} framework can be used in wide range of situations
where translation-based help is required.

We presented a powerful and flexible help system ``ExpandHelp''
constructed on the generate-and-filter algorithm, where
the system generates all the possible expressions of
help entries expanded from regular expressions given by the help data provider,
while the output expressions are filtered by search keywords using
an efficient approximate pattern matching algorithm.
Since the data format is simple and the search algorithm is fast and flexible,
developers can easily publish useful help data, while
users can have bigger chances of finding an appropriate
data from vague knowledges.

% References must be the same font size as other body text.
% そうなん?
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{paper}
